%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Technology Solution Delivery Intern} % Job title
  {Ernst \& Young Solutions LLP} % Organization
  {Singapore} % Location
  {Aug 2022 – Apr 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Supported the preparation of documents and oral presentations for project proposals in RFP contract bidding.}
      \item {Assisted in testing and amending configurations for SAP modules (e.g., Concur, FICO, RE-FX).}
      \item {Prepared walkthroughs to guide UAT users in testing deliverable SAP modules.}
      \item {Assisted Project Managers in monitoring project timelines, generating progress reports, etc.} \vspace{5mm}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Process Automation Intern} % Job title
  {Venture Corporation Limited} % Organization
  {Singapore} % Location
  {May 2021 – Aug 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Collaborated with team to gather requirements and addressed follow-ups for a project to automate the collection of visitors' information upon entering the compound, reducing contact between visitors and security staff during the COVID lockdown.}
      \item {Filtered SAP weekly material management reports and developed scripts to automate data massaging and visualisation of key report details, saving staff hours of weekly effort.} \vspace{5mm}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Enterprise System Management Intern} % Job title
  {CapitaLand} % Organization
  {Singapore} % Location
  {Mar 2019 – Aug 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Supported the implementation of system configuration changes in the SAP RE-FX module and conducted user acceptance testing (UAT) with users, assisting them in adapt to the new changes.}
      \item {Managed learning resources and documentation on the corporate learning portal to ensure technical specifications were up to date, making it easier for staff to find solutions to system related issues.} \vspace{5mm}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
