%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    %---------------------------------------------------------
    \cventry
    {Personal Media Management Platform for Organizing Audio Libraries} % Role
    {Audiolibrary} % Project Name
    {Singapore} % Location
    {Feb 2025 – Current} % Date(s)
    {
        \begin{cvitems} % Description(s) bullet points
            \item {Developing a modern audio library manager using Flask with SQLite database and Angular with Tailwind CSS, packaged using Electron.}
            \item {Configurable library management with database-persisted user preferences, and metadata scanning system that processes audio files.}
            \item {Implemented virtual scrolling using Angular CDK and incremental loading patterns for performance optimization, to ensure performance handling thousands of tracks while maintaining UI responsiveness.}
            \item {Utilises concurrent processing with background threading for CPU-intensive tasks and implemented reactive data flow using RxJS observables to maintain real-time UI updates.}
            \vspace{3mm}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Smart Student-Supervisor Matching for Capstone Project} % Role
    {Capstone Connect} % Project Name
    {Singapore} % Location
    {Apr 2024 – Jul 2024} % Date(s)
    {
        \begin{cvitems} % Description(s) bullet points
            \item {Engineered and deployed a prototype full-stack application (React, MongoDB, Express, Node.js) on Vercel with CI/CD pipeline, designed to efficiently handle matching for 300+ students and 50+ faculty members.}
            \item {Transformed a manual, subjective matching process into an automated system that reduced matching time to minutes while improving compatibility outcomes by analysing research interest alignment.}
            \item {Implemented text processing through tokenisation and Jaccard similarity algorithms to quantify matches between student proposals and faculty research areas, with match optimization using Gale-Shapley's and Hungarian algorithms to maximize overall fit scores.}
            \vspace{3mm}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Internet of Things Worksite Monitoring} % Role
    {Worksite Environmental Monitoring} % Project Name
    {Singapore} % Location
    {Sep 2021 – Apr 2022} % Date(s)
    {
        \begin{cvitems} % Description(s) bullet points
            \item {Comprehensive IoT monitoring solution capturing critical environmental parameters (temperature, humidity, noise) across multiple construction zones, enabling real-time hazard prevention through an interactive .NET/React dashboard}
            \item {Designed and implemented a resilient sensor network using multiple Raspberry Pi units with environmental sensors communicating via MQTT protocol, ensuring reliable data collection even in challenging worksite conditions.}
            \item {Built a complete data pipeline from sensor capture through RESTful APIs to PostgreSQL database, featuring data validation, automated alerts, and historical trend analysis for safety compliance reporting.}
            \item {Led bi-monthly demonstrations with industry partner, incorporating feedback to meet requirements and delivering a production-ready solution with comprehensive technical documentation.}
            \vspace{3mm}
        \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}
